Learning Causally-Generated Stationary Time Series

### 2017-02-24 doc/paper.tex
Updated figures and prior over PSD + connection to experiments

% Break in equations...
% \allowdisplaybreaks

@@

\Cref{mod:cgpcm2} reveals the CGCPM as a Gaussian process in which the kernel, or equivalently the power spectral density (PSD), is modelled nonparametrically. \Cref{fig:interpolation} illustrates the generative process of the CGPCM: First, a filter $h$ is generated. Then, the kernel $k_{f\cond h}$ is constructed. Finally, a sample $f\cond h$ is drawn from $\mathcal{GP}(0,k_{f \cond h}(t-t'))$. \Cref{fig:prior} visualises the corresponding prior over kernels.

@@

 \begin{figure}[t]
    \centering
    \begin{tabularx}{\linewidth}{>{\centering}X>{\centering}X}
        GPCM & CGPCM
    \end{tabularx}
    \includegraphics[width=\linewidth, height=3cm]{resources/prior.pdf}
    \caption{Prior distribution over kernels in the GPCM and CGPCM}
    \label{fig:prior}
\end{figure}

@@

\begin{figure*}[t]
    % \vskip 0.2in
    \centering
    \includegraphics[width=\linewidth]{resources/interpolation.pdf}
    \caption{Generative process of the CGPCM. Shows the filter $h$, the kernel $k_{f\cond h}$, and a sample $f\cond h \sim \mathcal{GP}(0,k_{f\cond h}(t-t'))$ while the filter is interpolated from one that satisfies $h(0)=0$ to one that satisfies $|h(0)|>0$.}
    \label{fig:interpolation}
    % \vskip -0.2in
\end{figure*}

@@

\Cref{fig:toy_causal_sample} shows the results for fitting the GPCM and CGPCM to instead a \textit{noiseless} random sample from the CGPCM. Since the drawn filter $h$ satisfies $|h(0)|>0$, the sample is rough and thus appears noisy. The challenge for the models is to not mistake this sample roughness for observation noise. Observe that the CGPCM fits the filter $h$ and kernel $k_{f \cond h}$ well, whereas GPCM's fit is mediocre. Despite roughly getting the correlation structure right, the GPCM mistakes the sample roughness for observation noise and provides a poor fit of the function $f\cond h$. The CGPCM, on the other hand, correctly recognises the sample roughness and provides an excellent fit of $f \cond h$. This discrepancy is explained by inspecting the fit of the PSD: the GPCM is unable to fit the higher frequencies in the sample, whereas the CGPCM does so succesfully.

>>>>

% Break in equations...
\allowdisplaybreaks

@@

\Cref{mod:cgpcm2} reveals the CGCPM as a Gaussian process in which the kernel, or equivalently the power spectral density (PSD), is modelled nonparametrically. \Cref{fig:interpolation} illustrates the generative process of the CGPCM: First, a filter $h$ is generated. Then, the kernel $k_{f\cond h}$ is constructed. Finally, a sample $f\cond h$ is drawn from $\mathcal{GP}(0,k_{f \cond h}(t-t'))$. \Cref{fig:prior} visualises the corresponding prior over kernels, and \cref{fig:prior_psd} visualises the corresponding prior over PSDs. Note that in \cref{fig:prior_psd} the prior for the GPCM has a low-pass structure, whereas that for the CGPCM decays more slowly.

@@

\begin{figure}[t]
    \centering
    \begin{tabularx}{\linewidth}{>{\centering}X>{\centering}X}
        GPCM & CGPCM
    \end{tabularx}
    \includegraphics[width=\linewidth, height=3cm]{resources/cropped/prior.pdf}
    \caption{Prior distribution over kernels in the GPCM and CGPCM. Lines correspond to means and gradients correspond to uncertainty.}
    \label{fig:prior}
\end{figure}

\begin{figure}[t]
    \centering
    \begin{tabularx}{\linewidth}{>{\centering}X>{\centering}X}
        GPCM & CGPCM
    \end{tabularx}
    \includegraphics[width=\linewidth, height=3cm]{resources/cropped/prior_psd.pdf}
    \caption{Prior distribution over PSDs in the GPCM and CGPCM. Lines correspond to means and gradients correspond to uncertainty.}
    \label{fig:prior_psd}
\end{figure}

@@

\begin{figure*}[t]
    \vskip 0.1in
    \centering
    \includegraphics[width=\linewidth]{resources/cropped/interpolation.pdf}
    \caption{Generative process of the CGPCM. Shows the filter $h$, the kernel $k_{f\cond h}$, and a sample $f\cond h \sim \mathcal{GP}(0,k_{f\cond h}(t-t'))$ while the filter is interpolated from one that satisfies $h(0)=0$ to one that satisfies $|h(0)|>0$.}
    \label{fig:interpolation}
    % \vskip -0.2in
\end{figure*}

@@

\Cref{fig:toy_causal_sample} shows the results for fitting the GPCM and CGPCM to instead a \textit{noiseless} random sample from the CGPCM. Since the drawn filter $h$ satisfies $|h(0)|>0$, the sample is rough and thus appears noisy. The challenge for the models is to not mistake this sample roughness for observation noise. Observe that the CGPCM fits the filter $h$ and kernel $k_{f \cond h}$ well, whereas GPCM's fit is mediocre. Despite roughly getting the correlation structure right, the GPCM mistakes the sample roughness for observation noise and provides a poor fit of the function $f\cond h$. The CGPCM, on the other hand, correctly recognises the sample roughness and provides an excellent fit of $f \cond h$. This discrepancy is explained by inspecting the fit of the PSD: the GPCM is unable to fit the higher frequencies in the sample, whereas the CGPCM does so succesfully; this is consistent with the priors depicted in \cref{fig:prior_psd}.
